### 2014-11-02 fundamentals/conclusion.tex

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible 
alternative to existing fuel cycles simulators.

Where, previous nuclear fuel cycle simulators have had limited distribution, 
uncertain provenance, and restricted customizability, \Cyclus emphasizes an 
open access and development strategy.  Open development, with transparent 
publication of the source code, not only provides much-needed accessibility, 
but also enables transparency and community oversight.

@@

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations 
at every level of detail. Simulations relying on arbitrarily complex isotopic 
compositions are possible in \Cyclus, as are simulations not employing any 
physics at all. Indeed, agents of such varying fidelity can even exist in the 
same simulation. Researchers no longer need to reinvent the wheel in order to 
model a simulation focused on the aspects of the fuel cycle that their research 
focuses on.

>>>>

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible 
alternative to existing fuel cycle simulators.

Where previous nuclear fuel cycle simulators have had limited distribution, 
uncertain provenance, and restricted customizability, \Cyclus emphasizes an 
open access and development strategy.  Open development, with transparent 
publication of the source code, not only provides much-needed accessibility, 
but also enables transparency and community oversight.

@@

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations 
at every level of detail. Simulations relying on arbitrarily complex isotopic 
compositions are possible in \Cyclus, as are simulations not employing any 
physics at all. Indeed, agents of such varying fidelity can even exist in the 
same simulation. Researchers no longer need to reinvent the wheel in order to 
model a simulation focused on the aspects of the fuel cycle
relevant to their research.
